On the probability of finding a nonphysical solution through shadowing

### 2020-11-06 main.tex
Change a few sentences too similar to scholarpedia.

\institute{           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           Center for Computational Science and Engineering, MIT, Cambridge, MA 02139, USA. \email{nishac@mit.edu 
		   }  \email{qiqi@mit.edu}
}

@@

The existence of arbitrarily long shadowing solutions for sufficiently similar governing equations
has been proven for invertible hyperbolic maps by Anosov \cite{anosov} and Bowen \cite{bowen}.
For non-hyperbolic systems, it is often possible to estimate the length of time for which shadowing
solutions exist \cite{grebogi}\cite{hammel}.

@@

>>>>

\institute{           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           Center for Computational Science and Engineering, MIT, Cambridge, MA 02139, USA. Corresponding author email: \email{nishac@mit.edu}  \email{qiqi@mit.edu}. Preprint available at \cite{preprint}
}

@@

When the slightly different governing equations are uniformly hyperbolic, it has been long know that infinitely 
long shadowing solutions exist \cite{anosov}\cite{bowen}.
Numerical experiments in non-hyperbolic systems have shown that shadowing
solutions may still exist \cite{grebogi}\cite{hammel} for finite amounts of time.

@@

\vspace{1in}

\textbf{Funding:} This work was supported by Air Force Office of Scientific Research Grant No. FA8650-19-C-2207.
\textbf{Conflict of Interest:} The authors declare that they have no conflict of interest.
